---
title: "Mouse CRPS Combined Cohorts 16S Analysis (Rarefied)"
author: "Rachel Rodgers"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
      code_folding: hide
runtime: shiny
editor_options:
    chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=8,
                      fig.height=6,
                      warning = FALSE,
                      message = FALSE)
```

```{r load-libraries, message=FALSE, include=FALSE}
library("shiny")
library("phyloseq")
library("vegan")
library("gridExtra")
library("knitr")
library("DESeq2")
library("plotly")
library("microbiome")
library("data.table")
library("ggrepel")
library("ggpubr")
library("scales")
library("plyr")
library("DT")
library("picante")
library("gridExtra")
library("tidyverse")

source("./shared_R_scripts/Helper_Functions.R")

options(shiny.sanitize.errors = FALSE)
```

## Overview {.tabset}

---

Analysis of combined mouse CRPS cohorts 1 (190809) and 2 (201019) using rarefied data.

Analyzed:

1. Comparison between separate cohorts by week:
  * control 1
  * control 2
  * treatment 1
  * treatment 2

2. Comparison between combined cohorts by week:
  * combined controls
  * combined treatments

3. Comparison within combined cohorts (across weeks)

----

```{r physeqBacteria, results='hide', include=FALSE}
physeqBacteriaNonRare <- readRDS("../data/physeqObjects/physeqBacteria_crps_combined_cohort.RDS")
physeqBacteria <- rarefy_even_depth(physeqBacteriaNonRare, rngseed = 54043710)
# rarefying dropped 290 taxa; reads dropped to 4,204
physeqBacteria # 877 x 207
```

```{r save-rarefied-data, eval=FALSE}
saveRDS(physeqBacteria, "../data/physeqObjects/physeqBacteria_rare.RDS")
```


```{r subset-physeqBacteria-by-week, include=FALSE}
sampleDataBacteria <- as(sample_data(physeqBacteria), "data.frame")

weeks = list("Week 0" = "week_0", "Week 3" = "week_3",
             "Week 5" = "week_5", "Week 9" = "week_9",
             "Week 16" = "week_16")

# Pull the sample names for each week so physeq object can be subsetted
sampleNameList <- pmap(.l = list(currWeek = weeks),
                       .f = function(df, currWeek) {
                         samples <- df %>% filter(week == currWeek) %>% 
                           pull(sample) %>% as.character()},
                       df = sampleDataBacteria)
```

### **16S Analysis: 4 Groups**

#### **Community Composition**

```{r subsetPhyseqBacteriaList}
# subset physeqBacteria by week, store in list
subsetPhyseqBacteriaList <- pmap(.l = list(sampleGroup = sampleNameList),
                                 .f = function(psObj, sampleGroup) {
                                   psSub <- psObj %>%
                                     prune_samples(samples = sampleGroup) %>%
                                     RemoveMissingTaxa()},
                                 psObj = physeqBacteria)
```

```{r comm-comp-4groups}

#----- UI -----#

inputPanel(
  # select physeq object by week
  selectInput(inputId = "commPhyseqObj4", label = "Week:", 
              choices = names(weeks),
              selected = "Week 0"),
  # select taxonomic rank
  selectInput(inputId = "commTaxRank4", label = "Taxonomic Rank:",
              choices = c("Kingdom", "Phylum", "Class", "Order", "Family",
                          "Genus", "Species"),
              selected = "Phylum"),
  # select abundance filter
  sliderInput(inputId = "abdFilter4", label = "Abundance Filter",
              min = 0, max = 1, step = 0.05, value = 0),
  # hide NA?
  checkboxInput(inputId = "hideNA4", label = "Hide unnamed taxa", value = FALSE)
)
# update
actionButton(inputId = "updateCommComp4", label = "Update Composition Plot",
             icon = icon("fas fa-sync-alt"))

#----- React -----#

CalculateAbundance <- eventReactive(input$updateCommComp4, {
  
  withProgress(message = "Calculating Abundance...", value = 1, {
                 abdDF <- MakeAbundanceDF(physeq = subsetPhyseqBacteriaList[[input$commPhyseqObj4]],
                                          taxRank = input$commTaxRank4,
                                          abundanceFilter = input$abdFilter4,
                                          pruneMissing = input$hideNA4)

                 if (dim(abdDF)[1] == 0) {
                   stop("No taxa meet this filtering criteria. 
                        Try lowering the Abundance Filter option.",
                        call. = FALSE)
                 } else {
                   if (input$commTaxRank4 == "Species") {
                     
                     abdDF <- mutate(abdDF,
                                     "GenusSpecies" = paste(Genus, Species, 
                                                            sep = " "),
                                     no = "other")
                   } # end of 2nd if/else
                 } # end of 1st if/else
                 abdDF # return object
               })# end of WithProgress()
}, ignoreNULL = FALSE) # end of eventReactive()


renderPlotly({
  compPlot <- PlotCommunityComposition(abdDF = CalculateAbundance(),
                                       taxRank = ifelse(isolate(input$commTaxRank4) == "Species",
                                                        yes = "GenusSpecies",
                                                        no = isolate(input$commTaxRank4)),
                                       facetFormula = "~ group")
  
  ggplotly(compPlot, height = 600, width = 1000)
})
```

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

#### **Alpha Diversity**

```{r alpha-div-idx}
alphaIdxList <- list("Richness" = "observed", "evenness" = "evenness_pielou",
                     "Shannon Diversity" = "diversity_shannon", 
                     "Faith's PD" = "PD")

alphaDiv <- microbiome::alpha(physeqBacteria, index = c("observed",
                                                        "evenness_pielou",
                                                        "diversity_shannon"))

faithsPD <- pd(as.data.frame(physeqBacteria@otu_table),
               physeqBacteria@phy_tree,
               include.root = FALSE)

allAlphaDiv <- merge(alphaDiv, faithsPD, by = "row.names", all = TRUE)
allAlphaDiv <- column_to_rownames(allAlphaDiv, var = "Row.names")

sampleDataBacteria <- merge(as(sample_data(physeqBacteria), "data.frame"), 
                            allAlphaDiv, by = "row.names", all = TRUE)
```

```{r save-sampleDataBacteria, echo=FALSE, include=FALSE, eval=FALSE}
write.table(sampleDataBacteria, 
            file = "../analysis/results/sampleData_withAlphaIdx.txt",
            quote = FALSE, sep = "\t", row.names = FALSE)

```

```{r alpha-div-4groups}

#----- UI -----#

inputPanel(
  selectInput(inputId = "alphaDiv4", label = "Week:", choices = weeks)
)

#----- React -----#

alphaDivDF4 <- reactive(
  filter(sampleDataBacteria, week == input$alphaDiv4)
)

alphaDivPlots4 <- reactive({
  pmap(.l = list(yVar = alphaIdxList,
                 yLab = names(alphaIdxList)),
       .f = PlotAlphaDiversity,
       df = alphaDivDF4(),
       xVar = "group",
       statMethod = "kruskal.test")
})

renderPlot({
  grid.arrange(alphaDivPlots4()[["Richness"]],
               alphaDivPlots4()[["Faith's PD"]],
               alphaDivPlots4()[["Shannon Diversity"]],
               ncol = 2,
               nrow = 2)
}, width = 900, height = 900)
br()
```

#### **Beta Diversity**

```{r beta-diversity-4groups}

#----- UI -----#

inputPanel(
  # select week
  selectInput(inputId = "pcoaPhyseqObject4", label = "Week:",
              choices = names(weeks)),
  # select distance method 
  radioButtons(inputId = "pcoaDistanceMethod4", label = "Distance Method:",
               choices = c("UniFrac" = "unifrac",
                           "Weighted UniFrac" = "wunifrac"),
               selected = "unifrac"),
  # include sample names as labels on the plot?
  checkboxInput(inputId = "pcoaShowLabels4", label = "Show point labels",
                value = FALSE),
  # want to see norm-type confidence ellipses?  they can be distracting
  checkboxInput(inputId = "pcoaShowEllipses4", 
                label = "Show confidence ellipses", value = TRUE)
)

#----- React -----#

CalculateOrdination4 <- reactive({
  withProgress(message = "Calculating ordination (4 groups)...", value = 1, {
    # Generate ordination object
    set.seed(20097511)
    ordinationObj <- ordinate(subsetPhyseqBacteriaList[[input$pcoaPhyseqObject4]],
                              method = "PCoA",
                              distance = input$pcoaDistanceMethod4)
  })
})

renderPlot({
  basePlot <- plot_ordination(subsetPhyseqBacteriaList[[isolate(input$pcoaPhyseqObject4)]],
                              ordination = CalculateOrdination4(),
                              color = "group", shape = "group") +
    scale_shape_manual(values = c(15, 16, 17, 18)) +
    theme_bw() +
    theme(legend.title = element_text(size = 18),
          legend.text = element_text(size = 16),
          axis.title.x = element_text(size = 14),
          axis.title.y = element_text(size = 14),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12)) +
    geom_point(size = 4)
  
  if (input$pcoaShowLabels4) {
    basePlot <- basePlot +
      geom_text_repel(aes_string(label = "sample"), color = "grey30", size = 4)
  }
  
  if (input$pcoaShowEllipses4 == TRUE) {
    basePlot <- basePlot + stat_ellipse(type = "norm")
  }
  
  basePlot
  
}, height = 600, width = 900)
```

**ADONIS Results for selected Week and Distance Measure:**

ADONIS is used to determine whether clustering on the PCoA plot is significant based on condition.

```{r beta-adonis-4groups}
renderPrint(
  RunAdonis(physeqObj = subsetPhyseqBacteriaList[[input$pcoaPhyseqObject4]],
            category = "group", distance = input$pcoaDistanceMethod4)
)
```

### **16S Analysis: 2 Groups**

#### **Community Composition**

```{r comm-comp-2groups}

#----- UI -----#

inputPanel(
  # select physeq object by week
  selectInput(inputId = "commPhyseqObj2", label = "Week:", 
              choices = names(weeks),
              selected = "Week 0"),
  # select taxonomic rank
  selectInput(inputId = "commTaxRank2", label = "Taxonomic Rank:",
              choices = c("Kingdom", "Phylum", "Class", "Order", "Family",
                          "Genus", "Species"),
              selected = "Phylum"),
  # select abundance filter
  sliderInput(inputId = "abdFilter2", label = "Abundance Filter",
              min = 0, max = 1, step = 0.05, value = 0),
  # hide NA?
  checkboxInput(inputId = "hideNA2", label = "Hide unnamed taxa", value = FALSE)
)
# update
actionButton(inputId = "updateCommComp2", label = "Update Composition Plot",
             icon = icon("fas fa-sync-alt"))

#----- React -----#

CalculateAbundance2 <- eventReactive(input$updateCommComp2, {
  
  withProgress(message = "Calculating Abundance...", value = 1, {
                 abdDF <- MakeAbundanceDF(physeq = subsetPhyseqBacteriaList[[input$commPhyseqObj2]],
                                          taxRank = input$commTaxRank2,
                                          abundanceFilter = input$abdFilter2,
                                          pruneMissing = input$hideNA4)

                 if (dim(abdDF)[1] == 0) {
                   stop("No taxa meet this filtering criteria. 
                        Try lowering the Abundance Filter option.",
                        call. = FALSE)
                 } else {
                   if (input$commTaxRank4 == "Species") {
                     
                     abdDF <- mutate(abdDF,
                                     "GenusSpecies" = paste(Genus, Species, 
                                                            sep = " "),
                                     no = "other")
                   } # end of 2nd if/else
                 } # end of 1st if/else
                 abdDF # return object
               })# end of WithProgress()
}, ignoreNULL = FALSE) # end of eventReactive()


renderPlotly({
  compPlot <- PlotCommunityComposition(abdDF = CalculateAbundance2(),
                                       taxRank = ifelse(isolate(input$commTaxRank2) == "Species",
                                                        yes = "GenusSpecies",
                                                        no = isolate(input$commTaxRank2)),
                                       facetFormula = "~ condition")
  
  ggplotly(compPlot, height = 600, width = 1000)
})
```

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

#### **Alpha Diversity**

```{r alpha-div-2groups}

#----- UI -----#

inputPanel(
  selectInput(inputId = "alphaDiv2", label = "Week:", choices = weeks)
)

#----- React -----#

alphaDivDF2 <- reactive(
  filter(sampleDataBacteria, week == input$alphaDiv2)
)

alphaDivPlots2 <- reactive({
  pmap(.l = list(yVar = alphaIdxList,
                 yLab = names(alphaIdxList)),
       .f = PlotAlphaDiversity,
       df = alphaDivDF2(),
       xVar = "condition",
       statMethod = "wilcox.test")
})

renderPlot({
  grid.arrange(alphaDivPlots2()[["Richness"]],
               alphaDivPlots2()[["Faith's PD"]],
               alphaDivPlots2()[["Shannon Diversity"]],
               ncol = 2,
               nrow = 2)
}, width = 900, height = 900)
br()
```

#### **Beta Diversity**

```{r beta-diversity-2groups}

#----- UI -----#

inputPanel(
  # select week
  selectInput(inputId = "pcoaPhyseqObject2", label = "Week:",
              choices = names(weeks)),
  # select distance method 
  radioButtons(inputId = "pcoaDistanceMethod2", label = "Distance Method:",
               choices = c("UniFrac" = "unifrac",
                           "Weighted UniFrac" = "wunifrac"),
               selected = "unifrac"),
    # select which variable to color the points by (radio button)
  radioButtons(inputId = "pcoaColorVar", label = "Color Points By:",
               choices = c("Condition" = "condition", "Cage" = "cage_cohort")),
  
  br(),
  # include sample names as labels on the plot?
  checkboxInput(inputId = "pcoaShowLabels2", label = "Show point labels",
                value = FALSE),
  # want to see norm-type confidence ellipses?  they can be distracting
  checkboxInput(inputId = "pcoaShowEllipses2", 
                label = "Show confidence ellipses", value = TRUE)
)

#----- React -----#

CalculateOrdination2 <- reactive({
  withProgress(message = "Calculating ordination (2 groups)...", value = 1, {
    # Generate ordination object
    set.seed(10890127)
    ordinationObj <- ordinate(subsetPhyseqBacteriaList[[input$pcoaPhyseqObject2]],
                              method = "PCoA",
                              distance = input$pcoaDistanceMethod2)
  })
})

renderPlot({
  basePlot <- plot_ordination(subsetPhyseqBacteriaList[[isolate(input$pcoaPhyseqObject2)]],
                              ordination = CalculateOrdination2(),
                              color = input$pcoaColorVar, shape = "condition") +
    scale_shape_manual(values = c(15, 16)) +
    theme_bw() +
    theme(legend.title = element_text(size = 18),
          legend.text = element_text(size = 16),
          axis.title.x = element_text(size = 14),
          axis.title.y = element_text(size = 14),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12)) +
    geom_point(size = 4)
  
  if (input$pcoaColorVar == "condition") {
    basePlot <- basePlot +
      scale_color_manual(values = c("blue", "red"))
  }
  
  if (input$pcoaShowLabels2) {
    basePlot <- basePlot +
      geom_text_repel(aes_string(label = "sample"), color = "grey30", size = 3.5)
  }
  
  if (input$pcoaShowEllipses2 == TRUE) {
    basePlot <- basePlot + stat_ellipse(type = "norm")
  }
  
  basePlot
  
}, height = 600, width = 900)
```

```{r static-ordination-weighted, eval=FALSE, echo=FALSE, fig.width=9, fig.height=6}
set.seed(10890127)

allOrdObj <- map(subsetPhyseqBacteriaList,
                 ~ ordinate(.x, method = "PCoA", distance = "wunifrac"))

OrdPlot <- function(physeqObj, ordObj) {
  plot_ordination(physeq = physeqObj, ordination = ordObj, 
                  color = "condition", shape = "condition") +
    theme_bw() +
    scale_color_manual(values = c("slateblue3", "firebrick1")) +
    theme(legend.text = element_text(size = 12),
          axis.title = element_text(size = 10),
          axis.text = element_text(size = 10),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_point(size = 2) + 
    stat_ellipse(type = "norm")
}

allOrdPlots <- pmap(.l = list(physeqObj = subsetPhyseqBacteriaList,
                              ordObj = allOrdObj),
                    .f = OrdPlot)

ggarrange(plotlist = allOrdPlots, labels = names(subsetPhyseqBacteriaList),
          ncol = 2, nrow = 3, common.legend = TRUE, 
          legend = "right",font.label = list(face = "plain", size = 10),
          hjust = -1.5, vjust = 2)


set.seed(10890127)
adonisValues <- map(subsetPhyseqBacteriaList, 
                    ~ RunAdonis(.x, category = "condition", distance = "wunifrac"))
```

```{r static-ordination-unweighted, eval=FALSE, echo=FALSE, fig.width=9, fig.height=6}
set.seed(10890127)

allOrdObj <- map(subsetPhyseqBacteriaList,
                 ~ ordinate(.x, method = "PCoA", distance = "unifrac"))

OrdPlot <- function(physeqObj, ordObj) {
  plot_ordination(physeq = physeqObj, ordination = ordObj, 
                  color = "condition", shape = "condition") +
    theme_bw() +
    scale_color_manual(values = c("slateblue3", "firebrick1")) +
    theme(legend.text = element_text(size = 12),
          axis.title = element_text(size = 10),
          axis.text = element_text(size = 10),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    geom_point(size = 2) + 
    stat_ellipse(type = "norm")
}

allOrdPlots <- pmap(.l = list(physeqObj = subsetPhyseqBacteriaList,
                              ordObj = allOrdObj),
                    .f = OrdPlot)

ggarrange(plotlist = allOrdPlots, labels = names(subsetPhyseqBacteriaList),
          ncol = 2, nrow = 3, common.legend = TRUE, 
          legend = "right",font.label = list(face = "plain", size = 10),
          hjust = -1.5, vjust = 2)


set.seed(10890127)
adonisValues <- map(subsetPhyseqBacteriaList, 
                    ~ RunAdonis(.x, category = "condition", distance = "unifrac"))
```

**ADONIS Results for selected Week and Distance Measure:**

ADONIS is used to determine whether clustering on the PCoA plot is significant based on group.

```{r beta-adonis-2groups}
renderPrint(
  RunAdonis(physeqObj = subsetPhyseqBacteriaList[[input$pcoaPhyseqObject2]],
            category = input$pcoaColorVar, distance = input$pcoaDistanceMethod2)
)
```

### **Biomarkers: 2 groups**

#### **Treatment versus Control**


```{r deseq-condition}

#----- UI -----#

inputPanel(
  # select week
  selectInput(inputId = "deseqPhyseqCondition", label = "week",
              choices = names(weeks)),
  
  radioButtons(inputId = "deseqSigThreshCondition", 
               label = "Significance Threshold:",
               choices = c("0.05", "0.1"), selected = "0.05")
)
actionButton(inputId = "updateDESeqCondition", label = "Update DESeq Analysis",
             icon = icon("fas fa-sync-alt"))

br()
br()

#----- React -----#

RunDESeqCondition <- eventReactive(input$updateDESeqCondition, {
  
  withProgress(message = "Conducting DESeq analysis by Condition", value = 1, {
    set.seed(53237386)
    GenerateDESeqResults(physeq = subsetPhyseqBacteriaList[[input$deseqPhyseqCondition]],
                         variable = "condition",
                         numerator = "fracture",
                         denominator = "control")
  })
}, ignoreNULL = FALSE)

GetDESeqResultsCondition <- reactive(
  GenerateDESeqResultsTable(physeq = subsetPhyseqBacteriaList
                            [[isolate(input$deseqPhyseqCondition)]],
                            sigThreshold = isolate(as.numeric(input$deseqSigThreshCondition)),
                            ddsResults = RunDESeqCondition())
)

renderPlotly({
  volcano <- PlotStaticVolcano(physeq = subsetPhyseqBacteriaList
                               [[isolate(input$deseqPhyseqCondition)]],
                               resultsDataTable = GetDESeqResultsCondition(),
                               sigThreshold = isolate(as.numeric(input$deseqSigThreshCondition)),
                               plotTitle = "Differentially Abundant Taxa
                               Control (- L2FC) vs Treatment (+ L2FC)")
  
  ggplotly(volcano, tooltip = c("Phylum", "Family", "Genus", "Species",
                                "log2FoldChange", "baseMean"),
           height = 550, width = 900)
})
```

<br>
<br>
<br>
<br>
<br>

#### **Acute (combined weeks 3 & 5) vs Chronic (combined weeks 9 & 16)**

```{r subset-only-crps, results='hide'}
crpsSamples <- sampleDataBacteria %>% 
  filter(crps_type %in% c("acute", "chronic")) %>% 
  pull(sample) %>% 
  as.character()

keepCRPS <- sampleDataBacteria$sample[(sampleDataBacteria$sample %in% crpsSamples)]

physeqCRPS <- physeqBacteria %>% 
  prune_samples(samples = as.character(keepCRPS)) %>% 
  RemoveMissingTaxa()

physeqCRPS # 632 x 83
```

```{r deseq-crps-type}

#----- UI -----#

inputPanel(
  radioButtons(inputId = "deseqSigThresh2", label = "Significance Threshold:",
               choices = c("0.05", "0.1"), selected = "0.05")
)
actionButton(inputId = "updateDESeq2", label = "Update DESeq Analysis",
             icon = icon("fas fa-sync-alt"))

br()
br()

#----- React -----#

RunDESeq <- eventReactive(input$updateDESeq2, {
  
  withProgress(message = "Conducting DESeq analysis by CRPS type", value = 1, {
    set.seed(47126435)
    GenerateDESeqResults(physeq = physeqCRPS,
                         variable = "crps_type",
                         numerator = "chronic",
                         denominator = "acute")
  })
}, ignoreNULL = FALSE)

GetDESeqResults <- reactive(
  GenerateDESeqResultsTable(physeq = physeqCRPS,
                            sigThreshold = isolate(as.numeric(input$deseqSigThresh2)),
                            ddsResults = RunDESeq())
)

renderPlotly({
  volcano <- PlotStaticVolcano(physeq = physeqCRPS,
                               resultsDataTable = GetDESeqResults(),
                               sigThreshold = isolate(as.numeric(input$deseqSigThresh2)),
                               plotTitle = "Differentially Abundant Taxa
                               Acute (- L2FC) vs Chronic (+ L2FC)")
  
  ggplotly(volcano, tooltip = c("Phylum", "Family", "Genus", "Species",
                                "log2FoldChange", "baseMean"),
           height = 550, width = 900)
})
```

### **Within-Group Analysis: 2 groups**

**Community Composition Within Combined Treatment Groups**

```{r subsetBacteriaTreatment}
# subset physeqBacteria by group, store in list
treatments <- list("control" = "control", "fracture" = "fracture")

samplesByTreatment <- pmap(.l = list(currTreatment = treatments),
                           .f = function(df, currTreatment) {
                             samples <- df %>% filter(condition == currTreatment) %>%
                               pull(sample) %>% as.character()},
                           df = sampleDataBacteria)

subsetPhyseqBacteriaTreatment <- pmap(.l = list(sampleGroup = samplesByTreatment),
                                      .f = function(psObj, sampleGroup) {
                                        psSub <- psObj %>%
                                          prune_samples(samples = sampleGroup) %>%
                                          RemoveMissingTaxa()},
                                      psObj = physeqBacteria)

```

```{r comm-comp-wn-groups}

#----- UI -----#

inputPanel(
  
  selectInput(inputId = "commPhyseqObjTreatment", label = "Group:", 
              choices = names(treatments),
              selected = "control"),
  
  selectInput(inputId = "commTaxRankTreatment", label = "Taxonomic Rank:",
              choices = c("Kingdom", "Phylum", "Class", "Order", "Family",
                          "Genus", "Species"),
              selected = "Phylum"),
  
  sliderInput(inputId = "abdFilterTreatment", label = "Abundance Filter",
              min = 0, max = 1, step = 0.05, value = 0),
  
  checkboxInput(inputId = "hideNATreatment", label = "Hide unnamed taxa", 
                value = FALSE)
)

#----- React -----#

CalculateAbundanceTreatment <- reactive({
  
  withProgress(message = "Calculating Abundance by Condition...",
               value = 1, {
                 abdDF <- MakeAbundanceDF(physeq = subsetPhyseqBacteriaTreatment[[input$commPhyseqObjTreatment]],
                                          taxRank = input$commTaxRankTreatment,
                                          abundanceFilter = input$abdFilterTreatment,
                                          pruneMissing = input$hideNATreatment)
                 
                 if (dim(abdDF)[1] == 0) {
                   stop("No taxa meet this filtering criteria. 
                        Try lowering the Abundance Filter option.",
                        call. = FALSE)
                 } else {
                   if (input$commTaxRankTreatment == "Species") {
                     
                     abdDF <- mutate(abdDF,
                                     "GenusSpecies" = paste(Genus, Species, 
                                                            sep = " "),
                                     no = "other")
                   } # end of 2nd if/else
                 } # end of 1st if/else
                 abdDF # return object
               })# end of WithProgress()
})


renderPlotly({
  compPlot <- PlotCommunityComposition(abdDF = CalculateAbundanceTreatment(),
                                       taxRank = ifelse(isolate(input$commTaxRankTreatment) == "Species",
                                                        yes = "GenusSpecies",
                                                        no = isolate(input$commTaxRankTreatment)),
                                       facetFormula = "~ week")
  
  ggplotly(compPlot, height = 600, width = 1000)
  
})

```

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

#### **Alpha Diversity Within Combined Treatment Groups**

```{r alpha-div-wn-groups}

#----- UI -----#

inputPanel(
  selectInput(inputId = "alphaGroup", label = "Treatment Group:",
              choices = names(treatments), selected = "control")
)

#----- React ------#

alphaDivGroupDF <- reactive(
  filter(sampleDataBacteria, condition == input$alphaGroup)
)

alphaDivGroupPlots <- reactive({
  pmap(.l = list(yVar = alphaIdxList,
                 yLab = names(alphaIdxList)),
       .f = PlotAlphaDiversity,
       df = alphaDivGroupDF(),
       xVar = "week",
       statMethod = "kruskal.test")
})

renderPlot({
  grid.arrange(alphaDivGroupPlots()[["Richness"]],
               alphaDivGroupPlots()[["Faith's PD"]],
               alphaDivGroupPlots()[["Shannon Diversity"]],
               ncol = 2,
               nrow = 2)
}, width = 900, height = 900)
```

<br>

#### **Beta Diversity**

**UniFrac PCoA Plots:**
  
```{r beta-diversity-wn-condition}

#---- UI -----#

inputPanel(
  # treatment group
  selectInput(inputId = "pcoaPhyseqObjectWN", label = "Treatment Group:",
              choices = c("control", "fracture"), selected = "control"),
  
  # distance method 
  radioButtons(inputId = "pcoaDistanceMethodWN", label = "Distance Method:",
               choices = c("UniFrac" = "unifrac",
                           "Weighted UniFrac" = "wunifrac"),
               selected = "unifrac"),
  
  # include sample names as labels on the plot?
  checkboxInput(inputId = "pcoaShowLabelsWN", label = "Show point labels",
                value = FALSE),
  
  # want to see norm-type confidence ellipses?  they can be distracting
  checkboxInput(inputId = "pcoaShowEllipsesWN", 
                label = "Show confidence ellipses", value = TRUE)
)

#----- React -----#

CalculateOrdinationWN <- reactive({
  withProgress(message = "Calculating ordination within groups...", 
               value = 1, {
                 # Generate ordination object
                 set.seed(87019796)
                 ordinationObj <- ordinate(subsetPhyseqBacteriaTreatment[[input$pcoaPhyseqObjectWN]],
                                           method = "PCoA",
                                           distance = input$pcoaDistanceMethodWN)
               })
})

renderPlot({
  basePlot <- plot_ordination(subsetPhyseqBacteriaTreatment[[isolate(input$pcoaPhyseqObjectWN)]],
                              ordination = CalculateOrdinationWN(),
                              color = "week",
                              shape = "week") +
    theme_bw() +
    theme(legend.title = element_text(size = 18),
          legend.text = element_text(size = 16),
          axis.title.x = element_text(size = 14),
          axis.title.y = element_text(size = 14),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12)) +
    geom_point(size = 4)
  
  if (input$pcoaShowLabelsWN) {
    basePlot <- basePlot +
      geom_text_repel(aes_string(label = "sample"),
                      color = "grey30", size = 4)
  }
  
  if (input$pcoaShowEllipsesWN == TRUE) {
    basePlot <- basePlot + stat_ellipse(type = "norm")
  }
  
  basePlot
  
}, height = 600, width = 900)
```

ADONIS Results for selected Week and Distance Measure:

```{r beta-wn-adonis}
renderPrint(
  RunAdonis(physeqObj = subsetPhyseqBacteriaTreatment[[input$pcoaPhyseqObjectWN]],
            category = "week", distance = input$pcoaDistanceMethodWN)
)
```

<br>

### Session Info

```{r session-info}
Sys.Date()
getwd()
sessionInfo()
```
